rubfuns
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/ropenscilabs/rubfuns.svg?branch=master)](https://travis-ci.org/ropenscilabs/rubfuns)


`rubfuns` is a bunch of fxns inspired from Ruby

## Installation

Development version

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("ropenscilabs/rubfuns")
```

```{r}
library('rubfuns')
```

Package API:

```{r echo=FALSE, results="asis"}
cat(paste(" -", paste(getNamespaceExports("rubfuns"), collapse = "\n - ")))
```

## examples

`take_while`

```{r}
x <- c(1, 2, 3, 4, 5, 0)
take_while(x, function(z) z < 3)
x <- c(1, 2, 3, 4, 9, -1)
take_while(x, function(z) z < 3)
```

`drop_while`

```{r}
x <- c(1, 2, 3, 4, 5, 0)
drop_while(x, function(z) z < 3)
x <- c(1, 2, 3, 4, 9, -1)
drop_while(x, function(z) z < 3)
```

`delete_at`

```{r}
x <- c(1, 2, 3, 4, 5, 0)
delete_at(x, 5)
delete_at(x, 4:5)
```

`delete_if`

```{r}
x <- c(1, 2, 3, 4, 5, 0)
delete_if(x, function(z) z > 2)
delete_if(x, function(z) z < 4)
```

`shift`

```{r}
x <- c(1, 2, 3)
shift(x)
shift(x, 1)
```

`unshift`

```{r}
x <- c(1, 2, 3)
unshift(x, 4)
```

## Meta

* License: MIT
* Get citation information for `rubfuns` in R doing `citation(package = 'rubfuns')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
